\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Notation

@@

Approximate Bayesian Computation (ABC), also known as likelihood-free inference,
is a set of Monte Carlo techniques for approximating a posterior distribution
without having to evaluate the likelihood function. Instead, the ability to
generate simulated data sets from the sampling distribution is required.
Since a sampling distribution must be specified, it is not the assumption of
a specific likelihood that is avoided (indeed, a sampling distribution and
a data set imply a particular likelihood function), rather that we cannot
evaluate it cheaply as a function of $\params$ and $\data$.

>>>>

The posterior distribution
\begin{align}
p(\params | \data) &= \frac{p(\params)p(\data | \params)}{p(\data)}\\
&= \frac{\pi(\params)L(\params)}{Z}
\end{align}

@@

Approximate Bayesian Computation (ABC), also known as likelihood-free inference,
is a set of Monte Carlo techniques for approximating a posterior distribution
without having to evaluate the likelihood function $L(\theta)$.

. Instead, the ability to
generate simulated data sets from the sampling distribution is required.
Since a sampling distribution must be specified, it is not the assumption of
a specific likelihood that is avoided (indeed, a sampling distribution and
a data set imply a particular likelihood function), rather that we cannot
evaluate it cheaply as a function of $\params$ and $\data$.
